---
title: "Invoice"
output: pdf_document
geometry: "left=3cm,right=2cm,top=0cm,bottom=2cm"
fontsize: 11pt
papersize: a4
params: 
  invoiceNumber: '2022-'
  lang: 1
---
```{r setup, message = F,echo=F,warning=F}
library(lubridate)
library(readr)
library(dplyr)
# sudo apt install texlive-latex-base
# tinytex::install_tinytex()
library(tinytex)

lan_idx <- as.numeric(params$lang)

#
# json load
#

jsonL    <- rjson::fromJSON(file = "input_address_bank.json")
jFieldsL <- rjson::fromJSON(file = "fieldNames.json")
jSalaryL <- rjson::fromJSON(file = "input_salary.json")
j3rdL    <- rjson::fromJSON(file = "input_fedex.json")
jSickL   <- rjson::fromJSON(file = "input_sick.json")
mainL    <- rjson::fromJSON(file = "main.json")

ed <-  ymd(mainL$endDate)
sm <- month(mainL$startDate,label = T)
smna <- month(mainL$startDate,label = T, abbr=F)
em <- month(mainL$endDate,label = T)
sdt <- day(mainL$startDate)
edt <- day(mainL$endDate)
sy <- year(mainL$startDate)
ey <- year(mainL$endDate)

inv_dt <- day(mainL$invoiceDate)
inv_m <- month(mainL$invoiceDate, label = T)
inv_y <- year(mainL$invoiceDate)

condition<- jSalaryL$originalCurrency==jSalaryL$finalCurrency

exchangeDestiny <- paste(j3rdL$destinationFEDEX, j3rdL$destinationCurrency
                            ,"/", mainL$exchangeUSDBRL
                            , "=")

dayPay <- jSalaryL$originalSalary/20

sickPay <-  jSickL$sickDays*dayPay*(jSickL$percentageSick/100)

nonSickDays <- jSickL$totalDays - jSickL$sickDays

nonSickPay <-  nonSickDays*dayPay

sickPlusNonSick <- nonSickPay + sickPay

sickPlusNonSick <- ifelse(jSickL$use_sick_option,
                          sickPlusNonSick,
                          jSalaryL$originalSalary)

exchangeOrigin <- ifelse( condition
                    ,""
                    ,paste(sickPlusNonSick,jSalaryL$originalCurrency
                            ,"/", mainL$exchangeUSDPLN
                            , "=")
)

result <- ifelse(condition,
                 sickPlusNonSick
                 , round(sickPlusNonSick/mainL$exchangeUSDPLN )
)

benefits <- ifelse(condition
                   ,jSalaryL$originalBenefits
                 , round(jSalaryL$originalBenefits/mainL$exchangeUSDPLN )
)

benefits <- ifelse(jSalaryL$`use_benefits (Remote fees)`
                   ,benefits
                 , 0
)

use_benefits <- jSalaryL$`use_benefits (Remote fees)`

PDB <- ifelse(condition
                   ,jSalaryL$originalPDB
                 , round(jSalaryL$originalPDB/mainL$exchangeUSDPLN )
)

PDB <- ifelse(jSalaryL$usePDB
                   , PDB
                 , 0)

FEDEXresult <- ifelse(j3rdL$use_FEDEX_option, 
                      round(j3rdL$destinationFEDEX/mainL$exchangeUSDBRL ),
                      0)

total <- result + benefits + PDB + FEDEXresult

result <- format(result, scientific = F)

FEDEXresult <- format(FEDEXresult, scientific = F)

total <- format(total, scientific = F)

```

\pagenumbering{gobble} 

\raggedright `r jFieldsL$invoiceNumber[lan_idx]`: `r params$invoiceNumber` \par

\raggedleft `r jFieldsL$consultantBusiness[lan_idx]`: `r jsonL$consultantBusiness`    
\raggedleft `r jsonL$consultantAddress1`  
\raggedleft `r jsonL$consultantAddress2`   
\raggedleft `r jsonL$consultantAddress3`   
\raggedleft `r jsonL$consultantCountry`    
\raggedleft `r jFieldsL$consultantPhone[lan_idx]` :  `r jsonL$consultantPhone` 

\raggedright `r jFieldsL$billTo[lan_idx]` \par  
 
`r jsonL$billTo1`  
`r jsonL$billTo2`  
`r jsonL$billTo3`  
`r jsonL$billTo4`  
`r jsonL$billTo5`  

\begin{flushright} 
`r jFieldsL$date[lan_idx]`:  `r inv_dt` `r inv_m` `r inv_y`  
\end{flushright} 

| `r jFieldsL$Services[lan_idx]` | `r jFieldsL$amount[lan_idx]` |
|------------------------|-----------:|
|`r jFieldsL$ConsultancyCharges[lan_idx]`|    | 
``` {r , results="asis", echo=F, eval=T}
cat(
paste0("|\\hspace{2mm}","",sdt," ", sm," ", sy," to ",edt," ", em," ", ey," |    |\n"),
paste0("|\\hspace{2mm}", "Delivery date: ",smna," ",sy, "|    |\n"),
if(jSickL$use_sick_option){
paste0("|\\hspace{2mm}",jFieldsL$sickdays[lan_idx],": ", jSickL$sickDays,"/",jSickL$totalDays,"|", sickPay," ", jSalaryL$originalCurrency,"|","\n")
},
if(jSickL$use_sick_option){
paste0("|\\hspace{2mm}", jFieldsL$otherdays[lan_idx],"",nonSickDays,"/",jSickL$totalDays,"|",nonSickPay," ", jSalaryL$originalCurrency,"|","\n")
},
paste0("|\\hspace{2mm}", "1 ", jFieldsL$month[lan_idx],": ", exchangeOrigin,"|",result," ", jSalaryL$finalCurrency,"|","\n")
,
  if(use_benefits){
    paste0("|",jFieldsL$benefits[lan_idx],"|",benefits," ",jSalaryL$finalCurrency,"|","\n")
  },
  if(jSalaryL$usePDB){
    paste0("|", jFieldsL$PDB[lan_idx],"|",PDB," ",jSalaryL$finalCurrency,"|","\n")
  },
  if(j3rdL$use_FEDEX_option){
    paste0("|", jFieldsL$FEDEX_deliveryCosts[lan_idx]," ", exchangeDestiny,"|",FEDEXresult," ", jSalaryL$finalCurrency,"|","\n")
  },
  paste0("| **TOTAL**  | **",total,"** ",jSalaryL$finalCurrency,"|")
, sep="")
```

&nbsp;  
&nbsp;  
\begin{flushright} 
`r jFieldsL$Signature[lan_idx]`
\end{flushright}

\Large  \textbf{`r jFieldsL$WireInstructions[lan_idx]`} / \normalsize `r jFieldsL$BankAccountInformation[lan_idx]`

``` {r , results="asis", echo=F, eval=jSalaryL$intermediaryBank} 
cat(paste0("\\large \\textbf{",jFieldsL$Intermediary[lan_idx],"} /"
, jFieldsL$CorrespondentBank[lan_idx],"\\textbf{ (Field 56):}  \n  ") )
cat(paste0("\\hspace{5mm}\\normalsize SWIFT: **",jsonL$intermediary_bank_swift,"**  \n") )    
cat(paste0("\\hspace{5mm}",jFieldsL$Name[lan_idx],": ",    jsonL$intermediary_bank_name,", ",jsonL$intermediary_bank_country,"  \n")  )
```

\large `r jFieldsL$Beneficiary[lan_idx]` \textbf{`r jFieldsL$Bank[lan_idx]`:}  
\normalsize \hspace{5mm} SWIFT: \textbf{`r jsonL$final_bank_swift`}  
``` {r , results="asis", echo=F, eval=T} 
if(jSalaryL$intermediaryBank) {
  cat(paste("\\hspace{5mm}"
            ,paste0("**"
                    ,paste(c(jsonL$final_bank_short_name
                             ," "
                             ,jFieldsL$Account[lan_idx])[jFieldsL$order[[lan_idx]] ],collapse=" ")
                    ," **"
                    , jFieldsL$with[lan_idx]
                    )
            ,jsonL$intermediary_bank_name
            ,":"
            ,paste0("**",jsonL$final_bank_account,"**  \n") 
            ) 
      )
} else {
  cat("<!-- avoid line break -->")
}
```
\hspace{5mm} `r jFieldsL$Name[lan_idx]`: \textbf{`r jsonL$final_bank_name`}  
\hspace{5mm} `r jFieldsL$Address[lan_idx]`: `r jsonL$final_bank_address`, `r jsonL$final_bank_country`  

\large\textbf{`r jFieldsL$consultantBusiness[lan_idx]` } / `r jFieldsL$BeneficiaryCustomer[lan_idx]` \textbf{}:  
\hspace{5mm} \normalsize `r jFieldsL$Name[lan_idx]`: `r jsonL$consultantBusiness`    
\hspace{5mm} IBAN: **`r jsonL$consultantIBAN`**  

<!-- \large `r jFieldsL$RemittanceInformation[lan_idx]` \textbf{(Field 70)}:   -->
<!-- \hspace{5mm} \normalsize `r jFieldsL$Includealso[lan_idx]` **invoice number**, **contract number** -->
