---
title: "Consultancy Invoice"

output: pdf_document
fontsize: 11pt
params: 
  name: 'Janki'
  date: 2018-10-21
  start_date: 2018-10-15
  end_date: 2018-10-20
  details_file: 'baseline\\details.csv'
  skip_days: 0
  bonus: 0
---
```{r setup, message = F,echo=F,warning=F}
library(lubridate)
library(readr)
library(dplyr)

details <- read_csv(params$details_file,col_types = cols(ac_no = col_character()))
df <- details %>% filter(name == params$name) %>% as.list()
sd <- ymd(params$start_date)
ed <-  ymd(params$end_date)
sm <- month(params$start_date,label = T)
em <- month(params$end_date,label = T)
sdt <- day(params$start_date)
edt <- day(params$end_date)
sy <- year(params$start_date)
ey <- year(params$end_date)


days <- ed - sd + 1 - as.integer(params$skip_days)
stipend <-as.numeric(df$salary)
amt <- as.integer(as.integer(days) * stipend) 

inv_dt <- day(params$date)
inv_m <- month(params$date, label = T)
inv_y <- year(params$date)
bonus <- as.numeric(params$bonus)

df$phone <- as.character(df$phone)
df$ac_no <- toString(df$ac_no)

sign_name <- paste0(params$name,".png")

total <- as.character(amt+bonus)
```


\begin{flushright} 
Consultant Name:  `r df$name`  \end{flushright}
\begin{flushright} 
Address:  `r df$addr_l1`  \end{flushright}
\begin{flushright}`r df$addr_l2`, `r df$addr_l3`\end{flushright}
\begin{flushright}
Contact No:  `r df$phone` 
\end{flushright} 
 
 
 Bill To, 
 
 Company Name
 
 Company Address Line 1
 
 Company Address Line 2
 
 Company Address Line 3
 
 **GSTIN: ABCXYZDEF** 
 
 Place of Supply: Bengaluru
 \begin{flushright} 
Date:  `r inv_dt` `r inv_m` `r inv_y`  
\end{flushright} 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; **Invoice -  `r  sdt` `r sm` `r sy` to `r edt` `r em` `r ey`**

|PARTICULARS|HSN/SAC Code|AMOUNT(INR)
|-----------|------------|-----------
|Consultancy Charges| | 
| `r  sdt` `r sm` `r sy` to `r edt` `r em` `r ey`| | 
|  `r days` days x `r as.character(stipend)` per day|  |`r as.character(amt)` INR
|  Bonus: `r as.character(bonus)` INR|  |`r as.character(bonus)` INR
|          |    |   |            |
| CGST @ 9%, SGST @ 9% | |NA
| 'OR' IGST @18%  ||NA
|          |    |   |            |
| **TOTAL** |     | **`r total` INR**|
 

 ```{r, out.width = "50px",fig.align='right' ,echo=F}

knitr::include_graphics(sign_name)
```

 
 Consultant Name: `r df$name`
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  Signature  
 

 **Bank Account Information** 
 
Beneficiary Name:  `r df$ben_name `  
Bank account name: `r df$bank_ac_name`  
Bank branch address:	`r df$bank_branch_addr`  
Account number `r df$ac_no`  
IFSC Code: 	`r df$ifsc_code`  
PAN: 	`r df$pan`  
GSTIN: `r df$gstin`  
 

                                                                