---
title: "Invoice"
output: pdf_document
geometry: "left=3cm,right=2cm,top=0cm,bottom=2cm"
fontsize: 11pt
papersize: a4
params: 
  invoiceNumber: ''
  lang: 1
---
```{r setup, message = F,echo=F,warning=F}
library(lubridate)
library(readr)
library(dplyr)
# sudo apt install texlive-latex-base
library(tinytex)

lan_idx <- as.numeric(params$lang)

# main
json_fields_list <- rjson::fromJSON(file = "json/fieldNames.json")
json_final_currency_list <- rjson::fromJSON(file = "json/final_currency_inv_date.json")

#
# bank and businesses
#
json_business_to_bill_list <- rjson::fromJSON(file = "json/business_to_bill.json")
json_consultant_account_list <- rjson::fromJSON(file = "json/consultant_account.json")
json_consultant_business_list <- rjson::fromJSON(file = "json/consultant_contact.json")

# special multiline - salary - days
json_salary_list <- rjson::fromJSON(file = "json/salary.json")


# oneliners
json_oneliners_list <- rjson::fromJSON(file = "json/oneline_costs.json")

# multiliners
json_grouped_list <- rjson::fromJSON(file = "json/grouped_costs.json")

# dates
sm <- month(json_salary_list$dates$start, label = TRUE)
smna <- month(json_salary_list$dates$start, label = TRUE, abbr = FALSE)
em <- month(json_salary_list$dates$end, label = TRUE)
sdt <- day(json_salary_list$dates$start)
edt <- day(json_salary_list$dates$end)
sy <- year(json_salary_list$dates$start)
ey <- year(json_salary_list$dates$end)

inv_dt <- day(json_final_currency_list$invoiceDate)
inv_m <- month(json_final_currency_list$invoiceDate, label = TRUE)
inv_y <- year(json_final_currency_list$invoiceDate)

# currencies
final_currency <- json_final_currency_list$final_currency
salary_currency <- json_salary_list$main$currency
salary_currency_text <- salary_currency

use_oneliners <- unlist(json_oneliners_list[grep("use", names(json_oneliners_list), value = T)])

oneliners_currencies_mixed <- unlist(json_oneliners_list[grep("currency", names(json_oneliners_list), value = T)])
oneliners_exchanges <- unlist(json_oneliners_list[grep("currency_exchange_to_Final_Currency",
  names(json_oneliners_list),
  value = TRUE
)])
oneliners_currencies <- oneliners_currencies_mixed[which(!names(oneliners_currencies_mixed) %in% names(oneliners_exchanges))]

oneliners_currencies_filtered <- oneliners_currencies[use_oneliners]
oneliners_values <- unlist(json_oneliners_list[grep("value", names(json_oneliners_list), value = T)])
oneliners_values_filtered <- oneliners_values[use_oneliners]

final_to_oneliners_exchange_conditions <- final_currency == oneliners_currencies_filtered

oneliners_texts <- unlist(json_oneliners_list[grep("text", names(json_oneliners_list), value = T)])
oneliners_texts_filtered <- oneliners_texts[use_oneliners]

oneliners_exchanges_filtered <- oneliners_exchanges[use_oneliners]
oneliners_exchanges_filtered_needed <- oneliners_exchanges_filtered[!final_to_oneliners_exchange_conditions]
oneliners_currency_texts <- oneliners_currencies_filtered

grouped_currency <- json_grouped_list$currency_grouped
grouped_currency_text <- grouped_currency

# currency exchanges comparisons booleans
final_to_salary_exchange_condition <- final_currency == salary_currency

final_to_grouped_exchange_condition <- final_currency == grouped_currency

if (final_to_salary_exchange_condition) {
  salary_currency_text <- ""
}

if (final_to_grouped_exchange_condition) {
  grouped_currency_text <- ""
}

use_dates <- json_salary_list$dates$use
use_salary_and_related <- json_salary_list$main$use_salary_and_related
use_period <- json_salary_list$period$use
use_modified <- json_salary_list$modified_days$use
use_nwd <- json_salary_list$non_working_days$use

use_grouped <- json_grouped_list$use_grouped

total_days <- json_salary_list$main$total_days

salary_periods <- json_salary_list$period$number

periods_string <- ifelse((salary_periods == 0 || salary_periods == "") || !use_period, "",
  paste0(salary_periods, " ", json_salary_list$period$name, ":")
)

day_pay <- json_salary_list$main$salary / total_days

modified_days <- ifelse(use_modified, json_salary_list$modified_days$days, 0)

non_working_days <- ifelse(use_nwd, json_salary_list$non_working_days$days, 0)

modified_pay <- modified_days * day_pay * (json_salary_list$modified_days$percentage / 100)

common_payable_days <- total_days - modified_days - non_working_days

common_payable_salary_days_pay <- common_payable_days * day_pay

common_plus_modified_pay <- common_payable_salary_days_pay + modified_pay
common_plus_modified_pay_rounded <- round(common_plus_modified_pay, 1)
common_payable_salary_days_pay_rounded <- round(common_payable_salary_days_pay, 1)

exchange_salary_text <- ifelse(final_to_salary_exchange_condition,
  "|",
  paste(
    common_plus_modified_pay_rounded, "|",
    "/", json_salary_list$main$currency_exchange_to_Final_Currency,
    "="
  )
)

salary_days_pay_final <- ifelse(final_to_salary_exchange_condition,
  common_plus_modified_pay,
  round(common_plus_modified_pay / json_salary_list$main$currency_exchange_to_Final_Currency)
)

modified_pay_rounded <- round(modified_pay, 1)

salary_days_pay_final <- ifelse(use_salary_and_related, salary_days_pay_final, 0)
oneliners_final <- 0

if (any(use_oneliners)) {
  oneliners_values_filtered_not_exchanged <- oneliners_values_filtered[final_to_oneliners_exchange_conditions]
  oneliners_texts_filtered_not_exchanged <- oneliners_texts_filtered[final_to_oneliners_exchange_conditions]

  oneliners_values_filtered_to_exchange <- oneliners_values_filtered[!final_to_oneliners_exchange_conditions]
  oneliners_currency_texts_needed <- oneliners_currency_texts[!final_to_oneliners_exchange_conditions]
  oneliners_texts_filtered_exchanged <- oneliners_texts_filtered[!final_to_oneliners_exchange_conditions]

  oneliners_values_filtered_exchanged <- round(oneliners_values_filtered_to_exchange / oneliners_exchanges_filtered_needed)
  oneliners_exchange_text <- paste(
    oneliners_values_filtered_to_exchange, "|", "/",
    oneliners_exchanges_filtered_needed, "="
  )
  oneliners_final <- sum(oneliners_values_filtered_not_exchanged, oneliners_values_filtered_exchanged)
}

grouped_final <- 0
grouped_items_text <- ""
exchange_grouped_text <- "|"
groupedCosts <- 0
total_grouped_finals_exchanged <- 0

if (use_grouped) {
  groupedCosts <- unlist(json_grouped_list[grep("Value", names(json_grouped_list), value = T)])

  if (final_to_grouped_exchange_condition) {
    grouped_final <- groupedCosts
  } else {
    grouped_final <- round(groupedCosts / json_grouped_list$currency_exchange_to_Final_Currency_Grouped)
  }

  grouped_items_text <- unlist(json_grouped_list[grep("^Name", names(json_grouped_list), value = T)])

  total_grouped_finals_exchanged <- sum(grouped_final)

  if (!final_to_grouped_exchange_condition) {
    exchange_grouped_text <- paste(
      format(sum(groupedCosts), scientific = FALSE), "|",
      "/", json_grouped_list$currency_exchange_to_Final_Currency_Grouped,
      "="
    )
  }
}

total_sum <- salary_days_pay_final + oneliners_final + total_grouped_finals_exchanged

total_pay_rounded <- round(total_sum)
total_pay_formatted_rounded <- format(total_pay_rounded, scientific = FALSE)

salary_days_pay_final_rounded <- round(salary_days_pay_final)
salary_days_pay_final_rounded_formatted <- format(salary_days_pay_final_rounded, scientific = FALSE)
grouped_final_formatted <- format(grouped_final, scientific = FALSE)
```

\pagenumbering{gobble} 

\raggedright `r json_fields_list$invoiceNumber[lan_idx]`: `r params$invoiceNumber` \par

\raggedleft `r json_fields_list$consultantBusiness[lan_idx]`: `r json_consultant_business_list$name`    
\raggedleft `r json_consultant_business_list$address1`  
\raggedleft `r json_consultant_business_list$address2`   
\raggedleft `r json_consultant_business_list$address3`   
\raggedleft `r json_consultant_business_list$country`    
\raggedleft `r json_fields_list$consultantPhone[lan_idx]` :  `r json_consultant_business_list$phone` 

\raggedright `r json_fields_list$billTo[lan_idx]` \par  
 
`r json_business_to_bill_list$billTo1`  
`r json_business_to_bill_list$billTo2`  
`r json_business_to_bill_list$billTo3`  
`r json_business_to_bill_list$billTo4`  
`r json_business_to_bill_list$billTo5`  

\begin{flushright} 
`r json_fields_list$date[lan_idx]`:  `r inv_dt` `r inv_m` `r inv_y`  
\end{flushright} 

| `r json_fields_list$Services[lan_idx]`| |  |   |  | `r json_fields_list$amount[lan_idx]` |
|--------|-------:|----|----:|----|-----------:|
|`r json_salary_list$main$section_title`|  |  | | | |
``` {r table, results="asis", echo=F, eval=T}
cat(
  if (use_dates) {
    paste0("|\\hspace{2mm}", "", sdt, " ", sm, " ", sy, " ", json_salary_list$dates$date_connector, " ", edt, " ", em, " ", ey, "| | |  |   |   |\n")
  },
  if (use_dates) {
    paste0("|\\hspace{2mm}", json_salary_list$dates$delivery_month_text, " ", smna, " ", sy, "| | |  |   |   |\n")
  },
  if (use_modified && use_salary_and_related) {
    paste0(
      "|\\hspace{8mm}", json_salary_list$modified_days$text, ": |", modified_days, "/", total_days, "|",
      "|", modified_pay_rounded, "|", salary_currency_text, "|  |", "\n"
    )
  },
  if ((use_modified | use_nwd) && use_salary_and_related) {
    paste0(
      "|\\hspace{8mm}", json_salary_list$main$common_days_text, "|", common_payable_days, "/", total_days, "|",
      "|", common_payable_salary_days_pay_rounded, "|", salary_currency_text, "|  |", "\n"
    )
  },
  if (use_salary_and_related) {
    paste0(
      "|\\hspace{2mm}", periods_string,
      "| |", salary_currency_text, "|", exchange_salary_text, "|", salary_days_pay_final_rounded_formatted, " ",
      final_currency, "|", "\n"
    )
  },
  if (any(use_oneliners)) {
    oneliners_strings <- c()
    for (idx in seq_along(oneliners_values_filtered_not_exchanged)) {
      oneliners_strings <- c(
        oneliners_strings,
        paste0("| | | | | \n"),
        paste0(
          "|", oneliners_texts_filtered_not_exchanged[idx],
          "| |", "|", "|", " ", "|", oneliners_values_filtered_not_exchanged[idx], " ",
          final_currency, "|", "\n"
        )
      )
    }
    for (idx in seq_along(oneliners_values_filtered_exchanged)) {
      oneliners_strings <- c(
        oneliners_strings,
        paste0("| | | | | \n"),
        paste0(
          "|", oneliners_texts_filtered_exchanged[idx], "| |", oneliners_currency_texts_needed[idx], "|",
          oneliners_exchange_text[idx],
          "|", " ", " ", oneliners_values_filtered_exchanged[idx], " ",
          final_currency, "|", "\n"
        )
      )
    }
    oneliners_strings
  },
  if (use_grouped) {
    grouped_strings <- character()
    for (grouped_idx in seq_along(grouped_final)) {
      grouped_strings <- c(
        grouped_strings,
        paste0(
          "|\\hspace{2mm}", grouped_items_text[grouped_idx], "| |", "|",
          " ", groupedCosts[grouped_idx], "|", grouped_currency_text, " ", "| |", "\n"
        )
      )
    }
    grouped_strings <- c(
      paste0("| | | | | \n"),
      grouped_strings,
      paste0(
        "|", json_grouped_list$GeneralName, "| |", grouped_currency_text, "|", exchange_grouped_text, "|", total_grouped_finals_exchanged, " ",
        final_currency, "|", "\n"
      )
    )
    grouped_strings
  },
  paste0("| | | | | \n"),
  paste0("| **TOTAL**  |   |   |   |   |**", total_pay_formatted_rounded, "** ", final_currency, "|"),
  sep = ""
)
```

&nbsp;  
&nbsp;  
\begin{flushright} 
`r json_fields_list$Signature[lan_idx]`
\end{flushright}

\Large  \textbf{`r json_fields_list$WireInstructions[lan_idx]`} / \normalsize `r json_fields_list$BankAccountInformation[lan_idx]`

``` {r intermediary, results="asis", echo=F, eval=json_consultant_account_list$use_intermediary} 
cat(paste0(
  "\\large \\textbf{", json_fields_list$Intermediary[lan_idx], "} /",
  json_fields_list$CorrespondentBank[lan_idx], "\\textbf{ (Field 56):}  \n  "
))
cat(paste0("\\hspace{5mm}\\normalsize SWIFT: **", json_consultant_account_list$intermediary_bank_swift, "**  \n"))
cat(paste0(
  "\\hspace{5mm}", json_fields_list$Name[lan_idx], ": ", json_consultant_account_list$intermediary_bank_name, ", ",
  json_consultant_account_list$intermediary_bank_country, "  \n"
))
```

\large `r json_fields_list$Beneficiary[lan_idx]` \textbf{`r json_fields_list$Bank[lan_idx]`:}  
\normalsize \hspace{5mm} SWIFT: \textbf{`r json_consultant_account_list$final_bank_swift`}  
``` {r bank, results="asis", echo=F, eval=T} 
if (json_consultant_account_list$use_intermediary) {
  cat(paste(
    "\\hspace{5mm}",
    paste0(
      "**",
      paste(c(
        json_consultant_account_list$final_bank_short_name,
        " ",
        json_fields_list$Account[lan_idx]
      )[json_fields_list$order[[lan_idx]]], collapse = " "),
      " **", json_fields_list$with[lan_idx]
    ),
    json_consultant_account_list$intermediary_bank_name,
    ":",
    paste0("**", json_consultant_account_list$final_bank_account, "**  \n")
  ))
} else {
  cat("<!-- avoid line break -->")
}
```
\hspace{5mm} `r json_fields_list$Name[lan_idx]`: \textbf{`r json_consultant_account_list$final_bank_name`}  
\hspace{5mm} `r json_fields_list$Address[lan_idx]`: `r json_consultant_account_list$final_bank_address`, `r json_consultant_account_list$final_bank_country`  

\large\textbf{`r json_fields_list$consultantBusiness[lan_idx]`} / `r json_fields_list$BeneficiaryCustomer[lan_idx]` \textbf{}:  
\hspace{5mm} \normalsize `r json_fields_list$Name[lan_idx]`: `r json_consultant_business_list$name`    
\hspace{5mm} IBAN: **`r json_consultant_account_list$IBAN`**  

<!-- \large `r json_fields_list$RemittanceInformation[lan_idx]` \textbf{(Field 70)}:   -->
<!-- \hspace{5mm} \normalsize `r json_fields_list$Includealso[lan_idx]` **invoice number**, **contract number** -->
